\documentclass[letterpaper, 12pt]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{microtype}

%% Sets page size and margins
\usepackage[top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\begin{document}

\section*{Please read carefully}

This Nondisclosure Agreement (this “Agreement”), effective of today’s date (“Effective Date”), is entered into by and between ${{companyname}}$, a ${{companytype}}$ corporation having offices at ${{companyaddress}}$ (“Company”) and yourself, (“Recipient”) (each herein referred to individually as a “Party”, or collectively as the “Parties”). In consideration of the covenants and conditions contained herein, the Parties hereby agree to the following:

\begin{enumerate}
    \item Purpose.\\
    The Parties wish to explore a business opportunity of mutual interest (the “Opportunity”), and in connection with the Opportunity, Company has disclosed, and may further disclose to Recipient certain confidential technical and business information that Company desires Recipient to treat as confidential.
    \item Confidential Information
    \begin{enumerate}
        \item Definition.\\ “Confidential Information” means any information disclosed by Company to Recipient, including any information disclosed prior to the Effective Date, either directly or indirectly in writing, orally or by inspection of tangible objects (including, without limitation, research, product plans, products, services, equipment, customers, markets, software, inventions, processes, designs, drawings, hardware, formulations, specifications, product configuration information, marketing and finance documents, prototypes, samples, data sets, equipment, white papers), whether or not designated as “confidential” at the time of disclosure. Confidential Information may also include information of a third party that is in Company’s possession and is disclosed to Recipient under this Agreement.
        \item Exceptions.\\
        Confidential Information shall not, however, include any information that Recipient can establish:
        \begin{enumerate}
            \item Was publicly known or made generally available without a duty of confidentiality prior to the time of disclosure to Recipient by Company;
            \item Becomes publicly known or made generally available without a duty of confidentiality after disclosure to Recipient by Company through no action or inaction of Recipient; or
            \item Is in the rightful possession of Recipient without confidentiality obligations at
the time of disclosure by Company to Recipient as shown by Recipient’s then-contemporaneous written files and records kept in the ordinary course of business.
        \end{enumerate} 
        \item Compelled Disclosure. \\
        If Recipient becomes legally compelled to disclose any Confidential Information, other than pursuant to a confidentiality agreement, Recipient will provide Company prompt written notice of such disclosure and will assist Company in seeking a protective order or another appropriate remedy. If Company waives Recipient’s compliance with this Agreement or fails to obtain a protective order or other appropriate remedy, Recipient will furnish only that portion of the Confidential Information that is legally required to be disclosed; provided that any Confidential Information so disclosed shall maintain its confidentiality protection for all purposes other than such legally compelled disclosure.
    \end{enumerate}
    \item Non-use and Non-disclosure.\\
    Recipient shall not use any Confidential Information for any purpose except to evaluate and engage in discussions concerning the Opportunity. Recipient shall not disclose any Confidential Information or permit any Confidential Information to be disclosed, either directly or indirectly, to any third party without Company’s prior written consent. Recipient shall not disclose Confidential Information or permit the disclosure of Confidential Information to its employees, except that Recipient may disclose Confidential Information to those employees of Recipient who are required to have the information in order for Recipient to evaluate or engage in discussions concerning the Opportunity; provided that such employee has signed a non-use and non-disclosure agreement in content at least as protective as the provisions hereof, prior to any disclosure of Confidential Information to such employee. Recipient shall not reverse engineer, disassemble, or decompile any prototypes, software, samples, or other tangible objects that embody the Confidential Information.
    \item Maintenance of Confidentiality.\\
    Recipient shall take reasonable measures to protect the secrecy of and avoid disclosure and unauthorized use of the Confidential Information. Without limiting the foregoing, Recipient shall take at least those measures it employs to protect its own most highly confidential information. Recipient shall not make any copies of the Confidential Information unless the same are previously
approved in writing by Company. Recipient shall reproduce Company’s proprietary rights notices on any such authorized copies, in the same manner in which such notices were set forth in or on the original. Recipient shall immediately notify Company of any unauthorized use or disclosure, or suspected unauthorized use or disclosure, of Confidential Information.
    \item No Obligation.\\
    Nothing in this Agreement shall obligate either Party to proceed with any transaction between them, and each Party reserves the
right, in its sole discretion, to terminate the discussions contemplated by this Agreement concerning the Opportunity. Nothing in this Agreement shall be construed to restrict Company’s use or disclosure of its own Confidential Information.
    \item No Warranty.\\
    ALL CONFIDENTIAL INFORMATION IS PROVIDED “AS IS.” COMPANY MAKES NO WARRANTIES, EXPRESS, IMPLIED OR OTHERWISE, REGARDING THE ACCURACY, COMPLETENESS OR PERFORMANCE OF ANY CONFIDENTIAL INFORMATION, OR WITH RESPECT TO NON-INFRINGEMENT OR OTHER VIOLATION OF ANY INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY OR OF RECIPIENT.
    \item Return of Materials.\\
    All documents and other tangible objects containing or representing Confidential Information and all copies or extracts thereof or notes derived therefrom that are in the possession or control of Recipient shall be and remain the property of Company and shall be promptly returned to Company or destroyed (with proof of such destruction), each upon Company’s request.
    \item No License.\\
    Nothing in this Agreement is intended to grant any rights to Recipient under any intellectual property right of Company, nor shall this Agreement grant Recipient any rights in or to the Confidential Information except as expressly set forth in this Agreement.
    \item Term.\\
    The obligations of Recipient under this Agreement shall survive until such time as all Confidential Information disclosed hereunder
becomes publicly known or made generally available through no action or inaction of Recipient.
    \item Remedies.\\
    Recipient agrees that any violation or threatened violation of this Agreement will cause irreparable injury to Company, entitling Company to obtain injunctive relief in addition to all legal remedies without showing or proving any actual damage and without any bond being required to be posted.
    \item Recipient.\\
    Information Company does not wish to receive any confidential information from Recipient, and Company assumes no obligation,
either expressed or implied, with respect to any information disclosed by Recipient to Company. Any ideas, suggestions, guidance
or other information disclosed by Recipient related to the Company’s business and any intellectual property rights relating to the
foregoing shall be collectively deemed “Feedback”. Company shall own all Feedback, and Recipient agrees to assign and hereby
assigns to Company all of its right, title, and interest in and to such Feedback. To the extent that the foregoing assignment is
ineffective for whatever reason, Recipient agrees to grant and hereby grants to Company a non-exclusive, perpetual, irrevocable,
royalty free, worldwide license (with the right to grant and authorize sub-licenses) to make, have made, use, import, offer for sale, sell, reproduce, distribute,
modify, adapt, prepare derivative works of, display, perform and otherwise exploit such Feedback without restriction.
    \item Miscellaneous.\\
    This Agreement shall bind and inure to the benefit of the Parties and their respective successors and permitted assigns; except that Recipient may not assign or otherwise transfer this Agreement, by operation of law or otherwise, (including by merger, reorganization, consolidation, change of control, or sale of all or substantially all of Recipient’s assets to which this Agreement pertains), without written consent of Company. Any assignment or transfer of this Agreement in violation of the foregoing shall be null and void. This Agreement will be interpreted and construed in accordance with the laws of the State of California, without regard to conflict of law principles. Recipient hereby represents and warrants that the persons executing this Agreement on its
behalf have express authority to do so, and, in so doing, to bind Recipient thereto. This Agreement contains the entire agreement between the Parties with respect to the Opportunity and supersedes all prior written and oral agreements between the Parties regarding the Opportunity. If a court or other body of competent jurisdiction finds any provision of this Agreement, or portion thereof, to be invalid or unenforceable, such provision will be enforced to the maximum extent permissible so as to effect the intent of the Parties, and the remainder of this Agreement will continue in full force and effect. No provision of this Agreement may be waived except by a writing executed by the Party against whom the waiver is to be effective. A Party’s failure to enforce any provision of this Agreement shall neither be construed as a waiver of the provision nor prevent the Party from enforcing any other provision of this Agreement. No provision of this Agreement may be amended or otherwise modified except by a writing signed by the Parties to this Agreement. The Parties may execute this Agreement in counterparts, each of which shall be deemed an original, but all of which together constitute one and the same agreement. This Agreement may be delivered by facsimile transmission, and facsimile copies of executed signature pages shall be binding as originals.
\end{enumerate}

\begin{flushright}
\textbf{Acknowledged and agreed on by signer(s) in the following signature pages:}\\ 

\vspace{5cm}
\Large[\emph{Space intentionally left blank}]
\end{flushright}


\end{document}